---
title: "PRIB Hackathon"
output: html_document
date: "2024-08-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries and setting working directory


```{r Chunk_1}
library(tidyverse)
library(ggplot2)
folder_path <- "/Users/ivanzamorano/Desktop/PRIB" # use your own path here
setwd(folder_path) # passing the object into the function
```

## Reading in the files


```{r Chunk_2}
background <- read_csv("assets_01d_background.csv")
consumption <- read_csv("assets_01d_background.csv")
durable_goods <- read_csv("assets_01d_background.csv")
food_consumption <- read_csv("assets_11a_foodconsumption_prod_purch.csv")
education <- read_csv("education_merged.csv")
```


## Merge data


```{r Chunk_3}

# Horizontal merge using merge function
merged_data_assets_1 <- merge(background, consumption, by = "FPrimary", all.x = TRUE)
merged_data_assets_2 <- merge(merged_data_assets_1, food_consumption, by = "FPrimary", all.x = TRUE )
#memory.limit(size = 32000)

#merged_data_assets_3 <- merge(merged_data_assets_2, food_consumption, by = "FPrimary", all.x = TRUE )

#merged_data_assets_education <- merge(merged_data_assets_3, education, by = "FPrimary", all.x = TRUE)


```


# Summaries 

```{r chunk_3.1}
summary(background) #Summary for background data
summary(consumption) #Summary for consumption data
summary(education) #Summary for education
summary(food_consumption) #Summary for food consumption

```
Merge por house id (variable FPimary)
Utilziar houseid, checar el father work y mother work distribución por región en nestlé 


#Father/Mother work plot: Ghana

```{r Chunk_4}
fatherwork_counts <- table(merged_data_assets_2$fatherwork.x)

# Create a pie chart for fatherwork
fatherwork_df <- as.data.frame(fatherwork_counts)
ggplot(fatherwork_df, aes(x = "", y = Freq, fill = Var1)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y", start = 0) +
  labs(title = "Fatherwork Categories") +
  theme_void()

# Count the categories for motherwork
motherwork_counts <- table(merged_data_assets_2$motherwork.x)

# Create a pie chart for motherwork
motherwork_df <- as.data.frame(motherwork_counts)
ggplot(motherwork_df, aes(x = "", y = Freq, fill = Var1)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y", start = 0) +
  labs(title = "Motherwork Categories") +
  theme_void()

```


## Father/mother work percentages: Ghana

```{r chunk_1223}
# Function to calculate percentages for a categorical variable
calculate_percentages <- function(counts) {
  percentages <- round(counts / sum(counts) * 100, 1)
  return(percentages)
}

# Count the categories and calculate percentages for fatherwork
fatherwork_counts <- table(merged_data_assets_2$fatherwork)
fatherwork_percentages <- calculate_percentages(fatherwork_counts)

# Count the categories and calculate percentages for motherwork
motherwork_counts <- table(merged_data_assets_2$motherwork)
motherwork_percentages <- calculate_percentages(motherwork_counts)

# Print the percentages for fatherwork
cat("Percentages for Fatherwork Categories:\n")
print(fatherwork_percentages)

# Print the percentages for motherwork
cat("Percentages for Motherwork Categories:\n")
print(motherwork_percentages)


```

#Ghana regions distribution


```{r chunk_6}
# Count the values for whereborn_region
whereborn_region_counts <- table(merged_data_assets_2$whereborn_region)

# Print the counts for whereborn_region
cat("Counts for Whereborn Region Categories:\n")
(whereborn_region_counts)

# Calculate percentages for whereborn_region
whereborn_region_percentages <- round(whereborn_region_counts / sum(whereborn_region_counts) * 100, 1)

# Print the percentages for whereborn_region
cat("Percentages for Whereborn Region Categories:\n")
whereborn_region_percentages
```

#Father/Mother work plot: Ghana by region (whereborn_region) - Northern

```{r chunk_7}
merged_data_assets_1 <- merge(background, consumption, by = "FPrimary", all.x = TRUE)
merged_data_assets_2 <- merge(merged_data_assets_1, food_consumption, by = "FPrimary", all.x = TRUE )

merged_data_assets_2

married <- subset(merged_data_assets_2, maritalstatus.x == "Married")

married_fatherwork_counts <- table(married$fatherwork)

# Create a pie chart for fatherwork
married_fatherwork_df <- as.data.frame(married_fatherwork_counts)
ggplot(married_fatherwork_df, aes(x = "", y = Freq, fill = Var1)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y", start = 0) +
  labs(title = "Fatherwork Categories") +
  theme_void()

# Count the categories for motherwork
married_motherwork_counts <- table(married$motherwork.x)

# Create a pie chart for motherwork
married_motherwork_df <- as.data.frame(married_motherwork_counts)
ggplot(motherwork_df, aes(x = "", y = Freq, fill = Var1)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y", start = 0) +
  labs(title = "Motherwork Categories") +
  theme_void()


# Count the categories and calculate percentages for fatherwork
married_fatherwork_percentages <- calculate_percentages(married_fatherwork_counts)

married_motherwork_percentages <- calculate_percentages(married_motherwork_counts)

# Print the percentages for fatherwork
cat("Percentages for Fatherwork Categories:\n")
print(married_fatherwork_percentages)

# Print the percentages for motherwork
cat("Percentages for Motherwork Categories:\n")
print(married_motherwork_percentages)
```



#Father/Mother work plot: Ghana by region (whereborn_region) - Ashanti 



#Father/Mother work plot: Ghana by region (whereborn_region) - Eastern 




#Father/Mother work plot: Ghana by region (whereborn_region) - Brong Ahafo 




Hacer el match de cuantos fathers y mothers hacen matching en los trabajos que tienen, hacer una matriz en donde se vea si están casados, etc,





```{r chunk_18}
merged_data_assets_1 <- merge(background, consumption, by = "FPrimary", all.x = TRUE)
merged_data_assets_2 <- merge(merged_data_assets_1, food_consumption, by = "FPrimary", all.x = TRUE )


merged_data_assets_2 <- merged_data_assets_2 %>%
  group_by(FPrimary) %>%
  mutate(Together = ifelse(maritalstatus == "Married" & n() > 1, 1, 0))


# Output the modified data frame
print(merged_data_assets_2)

# Now the Together column will contain 1 where the conditions are met, otherwise 0
Tog<-merged_data_assets_2$Together

summary(Tog)

Tog

Married_tog <- subset(merged_data_assets_2, Together == "1")

married_tog_fatherwork_counts <- table(Married_tog$fatherwork)

# Create a pie chart for fatherwork
married_tog_fatherwork_df <- as.data.frame(married_tog_fatherwork_counts)
ggplot(married_tog_fatherwork_df, aes(x = "", y = Freq, fill = Var1)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y", start = 0) +
  labs(title = "Fatherwork Categories") +
  theme_void()

# Count the categories for motherwork
married_tog_motherwork_counts <- table(Married_tog$motherwork)

# Create a pie chart for motherwork
married_tog_motherwork_df <- as.data.frame(married_tog_motherwork_counts)
ggplot(married_motherwork_df, aes(x = "", y = Freq, fill = Var1)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y", start = 0) +
  labs(title = "Motherwork Categories") +
  theme_void()


# Count the categories and calculate percentages for fatherwork
married_tog_fatherwork_percentages <- calculate_percentages(married_tog_fatherwork_counts)

married_tog_motherwork_percentages <- calculate_percentages(married_tog_motherwork_counts)

# Print the percentages for fatherwork
cat("Percentages for Fatherwork Categories:\n")
print(married_tog_fatherwork_percentages)

# Print the percentages for motherwork
cat("Percentages for Motherwork Categories:\n")
print(married_tog_motherwork_percentages)

```





```{r chunk_101}

merged_data_assets_1 <- merge(background, consumption, by = "FPrimary", all.x = TRUE)
merged_data_assets_2 <- merge(merged_data_assets_1, food_consumption, by = "FPrimary", all.x = TRUE )


#DIVORCED
merged_data_assets_2 <- merged_data_assets_2 %>%
  group_by(FPrimary) %>%
  mutate(Together = ifelse(maritalstatus == "Divorced"  & n() > 1, 1, 0))


# Output the modified data frame
print(merged_data_assets_2)

# Now the Together column will contain 1 where the conditions are met, otherwise 0
Tog<-merged_data_assets_2$Together

summary(Tog)

Tog

Married_tog <- subset(merged_data_assets_2, Together == "1")

married_tog_fatherwork_counts <- table(Married_tog$fatherwork)

# Create a pie chart for fatherwork
married_tog_fatherwork_df <- as.data.frame(married_tog_fatherwork_counts)
ggplot(married_tog_fatherwork_df, aes(x = "", y = Freq, fill = Var1)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y", start = 0) +
  labs(title = "Fatherwork Categories") +
  theme_void()

# Count the categories for motherwork
married_tog_motherwork_counts <- table(Married_tog$motherwork)

# Create a pie chart for motherwork
married_tog_motherwork_df <- as.data.frame(married_tog_motherwork_counts)
ggplot(married_motherwork_df, aes(x = "", y = Freq, fill = Var1)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y", start = 0) +
  labs(title = "Motherwork Categories") +
  theme_void()


# Count the categories and calculate percentages for fatherwork
married_tog_fatherwork_percentages <- calculate_percentages(married_tog_fatherwork_counts)

married_tog_motherwork_percentages <- calculate_percentages(married_tog_motherwork_counts)

# Print the percentages for fatherwork
cat("Percentages for Fatherwork Categories:\n")
print(married_tog_fatherwork_percentages)

# Print the percentages for motherwork
cat("Percentages for Motherwork Categories:\n")
print(married_tog_motherwork_percentages)

```





```{r chunk_8}

merged_data_assets_1 <- merge(background, consumption, by = "FPrimary", all.x = TRUE)
merged_data_assets_2 <- merge(merged_data_assets_1, food_consumption, by = "FPrimary", all.x = TRUE )

#SINGLE = 18

mean_age_married <- merged_data_assets_2 %>%
  filter(maritalstatus.x == "Married") %>%
  summarize(mean_age = mean(age.x, na.rm = TRUE))

# Print the result
print(mean_age_married)
#46



# Assuming merged_data_assets_2 is a data frame with columns age and maritalstatus

# Create the 'Single_household' column based on the specified conditions
merged_data_assets_2 <- merged_data_assets_2 %>%
  mutate(Single_household = ifelse(age.x > 18 & maritalstatus.x == "Never married", 1, 0))

# Output the modified data frame
print(merged_data_assets_2)

# Now the Together column will contain 1 where the conditions are met, otherwise 0
Sing <-merged_data_assets_2$Single_household

summary(Sing)

Sing

Sing_hh <- subset(merged_data_assets_2, Single_household == "1")


sing_fatherwork_counts <- table(Sing_hh$fatherwork.x)

# Create a pie chart for fatherwork
sing_fatherwork_df <- as.data.frame(sing_fatherwork_counts)
ggplot(sing_fatherwork_df, aes(x = "", y = Freq, fill = Var1)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y", start = 0) +
  labs(title = "Fatherwork Categories") +
  theme_void()


# Count the categories for motherwork
sing_motherwork_counts <- table(Sing_hh$motherwork.x)

# Create a pie chart for motherwork
sing_motherwork_df <- as.data.frame(sing_motherwork_counts)
ggplot(sing_motherwork_df, aes(x = "", y = Freq, fill = Var1)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y", start = 0) +
  labs(title = "Motherwork Categories") +
  theme_void()


# Count the categories and calculate percentages for fatherwork
sing_fatherwork_percentages <- calculate_percentages(sing_fatherwork_counts)

sing_motherwork_percentages <- calculate_percentages(sing_motherwork_counts)

# Print the percentages for fatherwork
cat("Percentages for Fatherwork Categories:\n")
print(sing_fatherwork_percentages)

# Print the percentages for motherwork
cat("Percentages for Motherwork Categories:\n")
print(sing_motherwork_percentages)

```

producedcedis is the overall production, not per unit 

```{r chunk_9}


merged_data_assets_1 <- merge(background, consumption, by = "FPrimary", all.x = TRUE)
merged_data_assets_2 <- merge(merged_data_assets_1, food_consumption, by = "FPrimary", all.x = TRUE )

#MARRIED 

merged_data_assets_2 <- merged_data_assets_2 %>%
  group_by(FPrimary) %>%
  mutate(TotalProducedCedis = sum(producedcedis, na.rm = TRUE)) %>%
  ungroup()


# Filter the data for maritalstatus == "MARRIED"
married_data <- merged_data_assets_2 %>%
  filter(maritalstatus.x == "Married")

# Group by FPrimary and calculate the sum of TotalProducedCedis
sum_data <- married_data %>%
  group_by(FPrimary) %>%
  summarise(SumTotalProducedCedis = sum(TotalProducedCedis, na.rm = TRUE)) %>%
  ungroup()

sum_data


# Plot the distribution using a histogram with adjusted x-axis limits
ggplot(sum_data, aes(x = SumTotalProducedCedis)) +
  geom_histogram(binwidth = 1000, fill = "blue", color = "black", alpha = 0.7) +
  theme_minimal() +
  labs(title = "Distribution of Produced Cedis for Married households",
       x = "Cedis",
       y = "Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlim(c(0, 50000)) +  # Set x-axis limits (adjust these values based on your data) 
  ylim(c(0, 100))  # Set y-axis limits (adjust these values based on your data)


```
```{r chunk_11}
merged_data_assets_1 <- merge(background, consumption, by = "FPrimary", all.x = TRUE)
merged_data_assets_2 <- merge(merged_data_assets_1, food_consumption, by = "FPrimary", all.x = TRUE )


merged_data_assets_2 <- merged_data_assets_2 %>%
  group_by(FPrimary) %>%
  mutate(TotalProducedCedis = sum(producedcedis, na.rm = TRUE)) %>%
  ungroup()


# Filter the data 
single_data <- merged_data_assets_2 %>%
  filter(Single_household == 1)

# Group by FPrimary and calculate the sum of TotalProducedCedis
sum_data_single <- single_data %>%
  group_by(FPrimary) %>%
  summarise(SumTotalProducedCedis = sum(TotalProducedCedis, na.rm = TRUE)) %>%
  ungroup()

sum_data_single


# Plot the distribution using a histogram with adjusted x-axis limits
ggplot(sum_data_single, aes(x = SumTotalProducedCedis)) +
  geom_histogram(binwidth = 1000, fill = "blue", color = "black", alpha = 0.7) +
  theme_minimal() +
  labs(title = "Distribution of Produced Cedis for Single households",
       x = "Cedis",
       y = "Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlim(c(0, 50000)) +  # Set x-axis limits (adjust these values based on your data) 
  ylim(c(0, 100))  # Set y-axis limits (adjust these values based on your data)


```





```{r chunk_122}

merged_data_assets_1 <- merge(background, consumption, by = "FPrimary", all.x = TRUE)
merged_data_assets_2 <- merge(merged_data_assets_1, food_consumption, by = "FPrimary", all.x = TRUE )


#SINGLE = 23.7 (World Bank)

mean_age_married <- merged_data_assets_2 %>%
  filter(maritalstatus.x == "Married") %>%
  summarize(mean_age = mean(age.x, na.rm = TRUE))

# Print the result
print(mean_age_married)
#46



# Assuming merged_data_assets_2 is a data frame with columns age and maritalstatus

# Create the 'Single_household' column based on the specified conditions
merged_data_assets_2 <- merged_data_assets_2 %>%
  mutate(Single_household = ifelse(age.x > 22 & maritalstatus.x == "Never married", 1, 0))

# Output the modified data frame
print(merged_data_assets_2)

# Now the Together column will contain 1 where the conditions are met, otherwise 0
Sing <-merged_data_assets_2$Single_household

summary(Sing)

Sing

Sing_hh <- subset(merged_data_assets_2, Single_household == "1")


sing_fatherwork_counts <- table(Sing_hh$fatherwork.x)

# Create a pie chart for fatherwork
sing_fatherwork_df <- as.data.frame(sing_fatherwork_counts)
ggplot(sing_fatherwork_df, aes(x = "", y = Freq, fill = Var1)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y", start = 0) +
  labs(title = "Fatherwork Categories") +
  theme_void()


# Count the categories for motherwork
sing_motherwork_counts <- table(Sing_hh$motherwork.x)

# Create a pie chart for motherwork
sing_motherwork_df <- as.data.frame(sing_motherwork_counts)
ggplot(sing_motherwork_df, aes(x = "", y = Freq, fill = Var1)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y", start = 0) +
  labs(title = "Motherwork Categories") +
  theme_void()


# Count the categories and calculate percentages for fatherwork
sing_fatherwork_percentages <- calculate_percentages(sing_fatherwork_counts)

sing_motherwork_percentages <- calculate_percentages(sing_motherwork_counts)

# Print the percentages for fatherwork
cat("Percentages for Fatherwork Categories:\n")
print(sing_fatherwork_percentages)

# Print the percentages for motherwork
cat("Percentages for Motherwork Categories:\n")
print(sing_motherwork_percentages)



merged_data_assets_2 <- merged_data_assets_2 %>%
  group_by(FPrimary) %>%
  mutate(TotalProducedCedis = sum(producedcedis, na.rm = TRUE)) %>%
  ungroup()


# Filter the data for maritalstatus == "MARRIED"
single_data <- merged_data_assets_2 %>%
  filter(Single_household == 1)

# Group by FPrimary and calculate the sum of TotalProducedCedis
sum_data_single <- single_data %>%
  group_by(FPrimary) %>%
  summarise(SumTotalProducedCedis = sum(TotalProducedCedis, na.rm = TRUE)) %>%
  ungroup()

sum_data_single


# Plot the distribution using a histogram with adjusted x-axis limits
ggplot(sum_data_single, aes(x = SumTotalProducedCedis)) +
  geom_histogram(binwidth = 1000, fill = "blue", color = "black", alpha = 0.7) +
  theme_minimal() +
  labs(title = "Distribution of Produced Cedis for Single households",
       x = "Cedis",
       y = "Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlim(c(0, 50000)) +  # Set x-axis limits (adjust these values based on your data) 
  ylim(c(0, 100))  # Set y-axis limits (adjust these values based on your data)


```


$Y_{it} = X_{it} + \gamma + Con_{it} + Educ_{it} + Con_{it}*Educ_{it} + \epsilon$


All 
|   |      Mother       |  Father  |
|----------|:-------------:|------:|
| Self employed farmer |  61.5 | 63.8 |
| Self employed trader |    24.8   | 4.9 |


Married
|   |      Mother       |  Father  |
|----------|:-------------:|------:|
| Self employed farmer |  68 | 77.4 |
| Self employed trader |    21.8   | 4.1 |




Single (Legal Age = 18)
|   |      Mother       |  Father  |
|----------|:-------------:|------:|
| Self employed farmer |  41.9 | 46 |
| Self employed trader |    41.1   | 6.9 |



Single (Mean Age = 23.7 World bank)
 
|   |      Mother       |  Father  |
|----------|:-------------:|------:|
| Self employed farmer |  41.2 | 44.4 |
| Self employed trader |    42.1   | 6.9 |

```{r chunk_1233}


# Install necessary packages if not already installed
install.packages("ggplot2")
install.packages("sf")
install.packages("rnaturalearth")
install.packages("rnaturalearthdata")

# Load the packages
library(ggplot2)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)

# Load map data for the world
world <- ne_countries(scale = "medium", returnclass = "sf")

# Filter to get only Ghana
ghana <- world[world$name == "Ghana", ]

# Plot the map of Ghana
ggplot(data = ghana) +
  geom_sf(fill = "lightblue", color = "black") +
  theme_minimal() +
  labs(title = "Map of Ghana",
       x = "Longitude",
       y = "Latitude")

# Plot with additional customization
ggplot(data = ghana) +
  geom_sf(fill = "lightgreen", color = "darkgreen") +
  theme_minimal() +
  labs(title = "Map of Ghana",
       subtitle = "Showing the boundaries of Ghana",
       x = "Longitude",
       y = "Latitude") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


```{r chunk_1211234}

merged_data_assets_1 <- merge(background, consumption, by = "FPrimary", all.x = TRUE)
merged_data_assets_2 <- merge(merged_data_assets_1, food_consumption, by = "FPrimary", all.x = TRUE )

#MARRIED 

merged_data_assets_2 <- merged_data_assets_2 %>%
  group_by(FPrimary) %>%
  mutate(TotalProducedCedis = sum(producedcedis, na.rm = TRUE)) %>%
  ungroup()


# Filter the data for maritalstatus == "MARRIED"
married_data <- merged_data_assets_2 %>%
  filter(maritalstatus.x == "Married")

# Group by FPrimary and calculate the sum of TotalProducedCedis
sum_data <- married_data %>%
  group_by(FPrimary) %>%
  summarise(SumTotalProducedCedis = sum(TotalProducedCedis, na.rm = TRUE)) %>%
  ungroup()

sum_data


# Plot the distribution using a histogram with adjusted x-axis limits
ggplot(sum_data, aes(x = SumTotalProducedCedis)) +
  geom_histogram(binwidth = 1000, fill = "blue", color = "black", alpha = 0.7) +
  theme_minimal() +
  labs(title = "Distribution of Produced Cedis for Married households",
       x = "Cedis",
       y = "Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlim(c(0, 50000)) +  # Set x-axis limits (adjust these values based on your data) 
  ylim(c(0, 100))  # Set y-axis limits (adjust these values based on your data)



merged_data_assets_1 <- merge(background, consumption, by = "FPrimary", all.x = TRUE)
merged_data_assets_2 <- merge(merged_data_assets_1, food_consumption, by = "FPrimary", all.x = TRUE )

#MARRIED 

merged_data_assets_2 <- merged_data_assets_2 %>%
  group_by(FPrimary) %>%
  mutate(TotalProducedCedis = sum(producedcedis, na.rm = TRUE)) %>%
  ungroup()


# Filter the data for maritalstatus == "MARRIED"
married_data <- merged_data_assets_2 %>%
  filter(maritalstatus.x == "Married")

# Group by FPrimary and calculate the sum of TotalProducedCedis
sum_data <- married_data %>%
  group_by(FPrimary) %>%
  summarise(SumTotalProducedCedis = sum(TotalProducedCedis, na.rm = TRUE)) %>%
  ungroup()

sum_data


# Plot the distribution using a histogram with adjusted x-axis limits
ggplot(sum_data, aes(x = SumTotalProducedCedis)) +
  geom_histogram(binwidth = 1000, fill = "blue", color = "black", alpha = 0.7) +
  theme_minimal() +
  labs(title = "Distribution of Produced Cedis for Married households",
       x = "Cedis",
       y = "Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlim(c(0, 50000)) +  # Set x-axis limits (adjust these values based on your data) 
  ylim(c(0, 100))  # Set y-axis limits (adjust these values based on your data)


```


```{r chunk_121434}
# Merge datasets
merged_data_assets_1 <- merge(background, consumption, by = "FPrimary", all.x = TRUE)
merged_data_assets_2 <- merge(merged_data_assets_1, food_consumption, by = "FPrimary", all.x = TRUE)

# Create the 'Single_household' column based on the specified conditions
merged_data_assets_2 <- merged_data_assets_2 %>%
  mutate(Single_household = ifelse(age.x > 18 & maritalstatus.x == "Never married", 1, 0))

# Calculate TotalProducedCedis
merged_data_assets_2 <- merged_data_assets_2 %>%
  group_by(FPrimary) %>%
  mutate(TotalProducedCedis = sum(producedcedis, na.rm = TRUE)) %>%
  ungroup()

# Filter the data for married and single households and calculate SumTotalProducedCedis
household_data <- merged_data_assets_2 %>%
  mutate(MaritalStatus = ifelse(Single_household == 1, "Single", maritalstatus.x)) %>%
  filter(MaritalStatus %in% c("Married", "Single"))

# Define bins for the cedis distribution
bins <- seq(0, 50000, by = 5000)  # Adjust bin width and range as needed

# Categorize TotalProducedCedis into bins
household_data <- household_data %>%
  mutate(CedisRange = cut(TotalProducedCedis, breaks = bins, include.lowest = TRUE, labels = FALSE))

# Count the frequency of households in each cedis range and marital status
distribution_data <- household_data %>%
  group_by(CedisRange, MaritalStatus) %>%
  summarise(Frequency = n()) %>%
  ungroup()

# Convert CedisRange to a factor with appropriate labels
distribution_data$CedisRange <- factor(distribution_data$CedisRange, 
                                       levels = 1:(length(bins) - 1),
                                       labels = paste(bins[-length(bins)], bins[-1], sep = "-"))

# Plot the clustered bar graph
ggplot(distribution_data, aes(x = CedisRange, y = Frequency, fill = MaritalStatus)) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +
  scale_fill_manual(values = c("Married" = "blue", "Single" = "red")) +
  theme_minimal() +
  labs(title = "Distribution of Produced Cedis for Married and Single Households",
       x = "Cedis Range",
       y = "Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


```



```{r chunk_664}
merged_data_assets_1 <- merge(background, consumption, by = "FPrimary", all.x = TRUE)
merged_data_assets_2 <- merge(merged_data_assets_1, food_consumption, by = "FPrimary", all.x = TRUE )


merged_data_assets_2 <- merged_data_assets_2 %>%
  group_by(FPrimary) %>%
  mutate(TotalProducedCedis = sum(producedcedis, na.rm = TRUE)) %>%
  ungroup()


# Filter the data 
single_data <- merged_data_assets_2 %>%
  filter(Single_household == 1)

# Group by FPrimary and calculate the sum of TotalProducedCedis
sum_data_single <- single_data %>%
  group_by(FPrimary) %>%
  summarise(SumTotalProducedCedis = sum(TotalProducedCedis, na.rm = TRUE)) %>%
  ungroup()

sum_data_single


# Plot the distribution using a histogram with adjusted x-axis limits
ggplot(sum_data_single, aes(x = SumTotalProducedCedis)) +
  geom_histogram(binwidth = 1000, fill = "blue", color = "black", alpha = 0.7) +
  theme_minimal() +
  labs(title = "Distribution of Produced Cedis for Single households",
       x = "Cedis",
       y = "Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlim(c(0, 50000)) +  # Set x-axis limits (adjust these values based on your data) 
  ylim(c(0, 100))  # Set y-axis limits (adjust these values based on your data)


merged_data_assets_1 <- merge(background, consumption, by = "FPrimary", all.x = TRUE)
merged_data_assets_2 <- merge(merged_data_assets_1, food_consumption, by = "FPrimary", all.x = TRUE )

#SINGLE = 18

mean_age_married <- merged_data_assets_2 %>%
  filter(maritalstatus.x == "Married") %>%
  summarize(mean_age = mean(age.x, na.rm = TRUE))

# Print the result
print(mean_age_married)
#46



# Assuming merged_data_assets_2 is a data frame with columns age and maritalstatus

# Create the 'Single_household' column based on the specified conditions
merged_data_assets_2 <- merged_data_assets_2 %>%
  mutate(Single_household = ifelse(age.x > 18 & maritalstatus.x == "Never married", 1, 0))
  
  
  -------------
  
  
  

merged_data_assets_1 <- merge(background, consumption, by = "FPrimary", all.x = TRUE)
merged_data_assets_2 <- merge(merged_data_assets_1, food_consumption, by = "FPrimary", all.x = TRUE )

#MARRIED 

merged_data_assets_2 <- merged_data_assets_2 %>%
  group_by(FPrimary) %>%
  mutate(TotalProducedCedis = sum(producedcedis, na.rm = TRUE)) %>%
  ungroup()


# Filter the data for maritalstatus == "MARRIED"
married_data <- merged_data_assets_2 %>%
  filter(maritalstatus.x == "Married")

# Group by FPrimary and calculate the sum of TotalProducedCedis
sum_data <- married_data %>%
  group_by(FPrimary) %>%
  summarise(SumTotalProducedCedis = sum(TotalProducedCedis, na.rm = TRUE)) %>%
  ungroup()

sum_data


# Plot the distribution using a histogram with adjusted x-axis limits
ggplot(sum_data, aes(x = SumTotalProducedCedis)) +
  geom_histogram(binwidth = 1000, fill = "blue", color = "black", alpha = 0.7) +
  theme_minimal() +
  labs(title = "Distribution of Produced Cedis for Married households",
       x = "Cedis",
       y = "Frequency") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlim(c(0, 50000)) +  # Set x-axis limits (adjust these values based on your data) 
  ylim(c(0, 100))  # Set y-axis limits (adjust these values based on your data)
```


```{r chunk_664}

# Assuming merged_data_assets_2 is the combined dataset with TotalProducedCedis calculated

# Create a new column 'HouseholdType' based on marital status
merged_data_assets_2 <- merged_data_assets_2 %>%
  mutate(HouseholdType = ifelse(Single_household == 1, "Single", 
                                ifelse(maritalstatus.x == "Married", "Married", "Other")))

# Filter only Single and Married households
filtered_data <- merged_data_assets_2 %>%
  filter(HouseholdType %in% c("Single", "Married"))

# Group by FPrimary and HouseholdType, calculate the sum of TotalProducedCedis
sum_data <- filtered_data %>%
  group_by(FPrimary, HouseholdType) %>%
  summarise(SumTotalProducedCedis = sum(TotalProducedCedis, na.rm = TRUE)) %>%
  ungroup()

# Plot the distribution using a histogram, differentiating by HouseholdType
ggplot(sum_data, aes(x = SumTotalProducedCedis, fill = HouseholdType)) +
  geom_histogram(binwidth = 1000, color = "black", alpha = 0.7, position = "identity") +
  theme_minimal() +
  labs(title = "Distribution of Produced Cedis for Single and Married households",
       x = "Cedis",
       y = "Frequency") +
  scale_fill_manual(values = c("Single" = "blue", "Married" = "green")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlim(c(0, 50000)) +  # Set x-axis limits (adjust these values based on your data)
  ylim(c(0, 100))  # Set y-axis limits (adjust these values based on your data)

```


```{r chunk_664}

# Assuming merged_data_assets_2 is the combined dataset with TotalProducedCedis calculated

# Create a new column 'HouseholdType' based on marital status
merged_data_assets_2 <- merged_data_assets_2 %>%
  mutate(HouseholdType = ifelse(Single_household == 1, "Single", 
                                ifelse(maritalstatus.x == "Married", "Married", "Other")))

# Filter only Single and Married households
filtered_data <- merged_data_assets_2 %>%
  filter(HouseholdType %in% c("Single", "Married"))

# Group by FPrimary and HouseholdType, calculate the sum of TotalProducedCedis
sum_data <- filtered_data %>%
  group_by(FPrimary, HouseholdType) %>%
  summarise(SumTotalProducedCedis = sum(TotalProducedCedis, na.rm = TRUE)) %>%
  ungroup()

# Plot the distribution using a histogram, differentiating by HouseholdType
ggplot(sum_data, aes(x = SumTotalProducedCedis, fill = HouseholdType)) +
  geom_histogram(binwidth = 1000, color = "black", alpha = 0.7, position = "dodge") +
  theme_minimal() +
  labs(title = "Distribution of Monthly Produced Cedis (₵) for Single and Married households",
       x = "Cedis (₵)",
       y = "Frequency") +
  scale_fill_manual(values = c("Single" = "blue", "Married" = "green")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlim(c(0, 50000)) +  # Set x-axis limits (adjust these values based on your data)
  geom_vline(xintercept = 2000, color = "red", linetype = "dashed", size = .7) +
  annotate("text", x = 2000, y = max(sum_data$Frequency) * 0.5, 
           label = "Ghana minimum living wage", color = "red", size = 3, 
           fontface = "bold", vjust = -35, hjust = -.2)


```
